Academic Advancement Advice: Author Articles as A.~A.

### 2018-03-14 trunk/citations/paper.tex
Compute worst papers

There are multiple hypothesized causes:

- When writing a last-minute ``related work'' section, authors seek
  out work

- Some academics try to \verb+fread+ all papers into memory, but
  it fails on the file that's just slightly larger than $2^{31}$ bytes,
  and so the papers therein don't get cited, and those papers are
  alphabetically in the middle or end of the alphabet.

% 
% 313779.  書評	29582	1	0.000068
% 313778.  インタビュー	20547	1	0.000097
% 313777.  facharzt	85315	9	0.000117
% 313776.  f3d	125257	15	0.000128
% 313775.  recenzja	63568	8	0.000142
% 313774.  newhaven	13296	1	0.000150
% 313773.  secrétaire	12267	1	0.000163
% 313772.  zahnarzt	17958	2	0.000167
% 313771.  libguides	389727	72	0.000187
% 313770.  硏究	12961	2	0.000231
% 313769.  그	15984	3	0.000250
% 313768.  kitas	7713	1	0.000259
% 313767.  シンポジウム	18539	4	0.000270
% 313766.  特集	878011	240	0.000274
%

>>>>

There are multiple hypothesized causes:
\begin{itemize}

\item When writing a last-minute ``related work'' section, authors
  sometimes find papers to cite in alphabetical order, for example, by
  reading another paper's bibliography, which is sometimes
  alphabetized.

\item Some academics try to \verb+fread+ all papers into memory, but
  it fails on the file that's just slightly larger than $2^{31}$ bytes,
  and so the papers therein don't get cited, and those papers are
  alphabetically in the middle or end of the alphabet.

\item When applying for grad school, tenure track faculty jobs, grants,
  and so on, packets are alphabetized ``for fairness,'' and the
  disposition of the committee becomes more irritable as they make
  progress through the set.

\end{itemize}

% 313779.  書評	29582	1	0.000068
% 313778.  インタビュー	20547	1	0.000097
% 313777.  facharzt	85315	9	0.000117
% 313776.  f3d	125257	15	0.000128
% 313775.  recenzja	63568	8	0.000142
% 313774.  newhaven	13296	1	0.000150
% 313773.  secrétaire	12267	1	0.000163
% 313772.  zahnarzt	17958	2	0.000167
% 313771.  libguides	389727	72	0.000187
% 313770.  硏究	12961	2	0.000231
% 313769.  그	15984	3	0.000250
% 313768.  kitas	7713	1	0.000259
% 313767.  シンポジウム	18539	4	0.000270
% 313766.  特集	878011	240	0.000274
%
